---
title: "Part 4 - Text"
author: "Robbert Batenburg"
date: "2024-04-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("C:/Users/robbe/OneDrive/uni/Master DSMA/Text Analysis/Assignment 1 RMarkdown")
```



Lastly, we have build a non-negative Matrix factorization (NMF) model to uncover latent topics within our reviews. Due to computational constraints, we used a subset of 2500 reviews for this analysis. We used the stemmed data set that has been cleaned from punctuation's. A NMF model extracts latent topics from a matrix, called a document-term matrix. First it decomposes the document-term matrix into a basis matrix and a coefficient matrix. The basis matrix include words that correspond to certain topics. The coefficient matrix include reviews that correspond to certain topics. We can use NMF to gain some general insights in common topics among the reviews of Disneyland.

We have made some choices when modeling the NMF algorithm. First, we had to determine which method we wanted to use to split our document-term matrix into basis and coefficient matrices. We used the "Lee" method, as this one performed relatively well among multiple metrics. the Lee model showed the lowest score on residuals and a relative high score on the silhouette coefficient. This indicates the lee model has less error and is better able to cluster reviews and words together based on the different topics. 

Secondly, we also had to decide on the number of topics the model should consider. The plot in Appendix C.1 shows how much of the residuals are explained by each additional topics considered in the model. It shows that the second added topic explains relatively a lot of the residual error. However, only using 2 factors for the analysis would not be very useful, as it results in very limited possibilities to gain insights. The seventh topic shows a slightly larger difference in explained residual error compared to all other topics afterwards, which is why we decide to only consider the first 7 factors for the NMF model. 


The multiple plots in Appendix C.2 show the 5 most important words for each of the 7 topics. The first topic contains the words Disneyland, Hong, Kong, staff and variations of experience. Comments containing this topic share general experience of Disneyland in Hong Kong and its staff. The fifth topic is very similar, but uses the word of Disney more general instead of Disneyland and uses the word world instead of staff. This topic seems to be more focused on the brand Disney in general. The second topic describes Disneyland as a theme park. The third topic is focusing on attractions and general experiences such as waiting time in the queues and the food. The fourth topic is about the duration of the visit, about the tickets and passes and about the characters in the parade. The sixth topic is specifically focused on time, usually involving waiting time in lines and queues. The last topic contain words about children who visited Disneyland. As enjoy is an important word in this topic, is seem that kids are usually positive about the attractions, the food and their visit in general. 

## Appendix C

```{r}
plotC.1 <- readRDS("plotC.1")

plot(plotC.1$d[1:20])

```

```{r}
plotC.2 <- readRDS("plotC.2")

plot(plotC.2)
```